### 2016-02-13 ch05-initvals/initial-values.tex
Some more comments of Johan addressed

@@

\begin{conjecture}\label{conj1}
The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e. $\model{0}$.
\end{conjecture}
\TODO{Johan: merk op dat dit niet zo hoeft te zijn! zelfs vanuit $\true{G}$ kan het misgaan}

@@

\subsection{Asymptotic runtime}
For the asymptotic runtime, we are mainly interested in how each of the smoothers scale with the size of the dataset, i.e. the number of samples $N$.

@@

Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
Using general methods, this is an operations that requires $\bigO{N^3}$ time.
% However, due to the Toeplitz structure~\citep{Heinig2011} of the regression matrix, this can be solved in $\bigO{N^2}$.

@@

\subsection{Implementation aspects}
\TODO{hint towards parallization}
\TODO{most costly: iteration}

>>>>

\begin{remark}
The \gls{LRM} has also been tried to generate better initial values.
However, given the discussion in \chapref{sec:nonparametric}, it is clear that the \gls{LRM} performs poorly in low \gls{SNR} situations.
The same was apparent from the quick trial we ran on \gls{LRM} starting values.
As such, the use of \gls{LRM} over \gls{LPM} offers no advantage for generation initial estimates.
\end{remark}

@@

\begin{conjecture}\label{conj1}
The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e. $\model{0}$.
\end{conjecture}
\begin{remark}
The use of $\true{G}$ as an initial estimation not necessarily entails in converging to the global optimum since it is not guaranteed that $\true{G}$ lies within the attraction region of the global optimum.
\end{remark}

@@

\subsection{Asymptotic runtime}
For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$.

@@

Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
Using general methods, this is an operations that requires $\bigO{N^3}$ time.

@@

\subsection{Implementation aspects}
This section discusses some implications and recommendations for the implementation of  a system identification toolbox.

Whereas \gls{RFIR} is shown to provide reliable starting values, it remains advisable to have multiple initialization strategies available to improve the likelihood of attaining a good starting value.
This is also the approach that toolboxes such as \citep{FDIDENT} and \citep{TDIDENT} employ.
Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e. one can easily try out a different strategy in parallel without incurring a lot of overhead.
As such, computing multiple starting values can happen without a significant increase in wall-clock time and consequently a sluggish user-experience.
